## Exercise 2: Motor Trend Car Road Tests

In this exercise, you will use the `mtcars` dataset from the `datasets` package. The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

__2.a__ Load the dataset mtcars. How many observations and variables does this dataset have?

```{r}
# 2.a

library(datasets)
data("mtcars")
summary(mtcars)
str(mtcars)
```

__2.b__ Print out the mtcars data frame sorted by hp (descending order).

```{r}
# 2.b

library(dplyr)
arrange(mtcars, desc(hp))
```

__2.c__ Create a new object named `cars_cyl` and assign to it the `mtcars` data frame grouped by the number of cylinders.

```{r}
# 2.c

cars_cyl <- mtcars
select(cars_cyl) %>%
group_by(cars_cyl$cyl) %>%
summarise(mpg=mean(cars_cyl$mpg),disp=mean(cars_cyl$disp), hp=mean(cars_cyl$hp), drat=mean(cars_cyl$drat), wt=mean(cars_cyl$wt), qsec=mean(cars_cyl$qsec), vs=mean(cars_cyl$vs), am=mean(cars_cyl$am), gear=mean(cars_cyl$gear), carb=mean(cars_cyl$carb))

# Use of tiblle might be easier ?tibble, sûrement faux :)
# Filter ??

```

__2.d__ Modify `cars_cyl` to remove all variables except the average miles/(US) gallon and gross horsepower for each cylinder group.

```{r}
# 2.d

cars_cyl[c(4,9)] %>%
group_by(cars_cyl$cyl)

```

__2.e__ Print out the average miles/(US) gallon and gross horsepower for each cylinder group.
What can you conclude about the effect of the number of cylinders on the other two variables?

```{r}
# 2.e
select(cars_cyl) %>%
group_by(cars_cyl$cyl) %>%
summarise(hp=mean(cars_cyl$hp),mpg=mean(cars_cyl$mpg))
```

__2.f__ Improve the summary statistics by also displaying the median, the minimum, the maximum, the standard deviation and the count.

```{r}
# 2.f

summary(cars_cyl, median(cars_cyl), min(cars_cyl), max(cars_cyl), sd(cars_cyl), count(cars_cyl))

# Sûrement faux, CHECK
```

__2.g__ Modify `cars_cyl` by adding a new variable called `perf = hp/mpg` and another
variable `rank` indicating the rank of the cars in terms of performance (the higher the better). 
Print out the resulting table by decreasing performance.

```{r}
# 2.g

mutate(cars_cyl,
perf = hp/mpg,
rank= max(perf),
desc(perf))
```

__2.h__ Print out the average performance for each 
number of cylinders. What can you say about the relationship between the two variables?

```{r}
# 2.h
carsperf <- group_by(cars_cyl, cyl)
summarise(carsperf, cars_cyl$perf)

# Pourquoi il trouve pas perf ? 
```

__2.i__ Using the full dataset, plot the relationship between the weight and miles per US gallon, with a different color for each number of cylinder. What can you conclude about the relationships between the three variables? Bonus: add a (linear) regression line for each group.

```{r}
# 2.i
LR <- lm(wt~ mpg , data = mtcars)
do (LR) {
  with(cars_cyl$cyl = 4, 6, 8)
    
  }

# Faire la regression par catégorie de cylindre 

```

__2.j__ Using the full dataset, plot the performance (gross horsepower divided by miles per US gallon) as a function of the weight, with a different color for each number of cylinders and a different shape for each type of transmission. What can you conclude about the relationships 
between the four variables?

```{r}
# 2.j
select(mtcars)
perf = mtcars$hp/mtcars$mpg

```

__2.k__ Save `cars_cyl` as a `.csv` into the `results` subdirectory in your project.

```{r}
# 2.k

save

```

