## Exercise 2: Motor Trend Car Road Tests

In this exercise, you will use the `mtcars` dataset from the `datasets` package. The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

__2.a__ Load the dataset mtcars. How many observations and variables does this dataset have?

```{r}
# 2.a

library(datasets)
data("mtcars")
summary(mtcars)
str(mtcars)
```

__2.b__ Print out the mtcars data frame sorted by hp (descending order).

```{r}
# 2.b

library(dplyr)
mtcars %>% arrange(desc(hp))  # Pipe down 
```

__2.c__ Create a new object named `cars_cyl` and assign to it the `mtcars` data frame grouped by the number of cylinders.

```{r}
# 2.c

cars_cyl <- mtcars %>%
group_by(cyl) %>%
arrange(cyl)


# Use of tiblle might be easier ?tibble, sûrement faux :)
# Filter ??

```

__2.d__ Modify `cars_cyl` to remove all variables except the average miles/(US) gallon and gross horsepower for each cylinder group.

```{r}
# 2.d

cars_cyl <- cars_cyl %>% group_by(cyl) %>% select(cyl, hp, mpg)

```

__2.e__ Print out the average miles/(US) gallon and gross horsepower for each cylinder group.
What can you conclude about the effect of the number of cylinders on the other two variables?

```{r}
# 2.e
cars_cyl %>%
select(cyl, hp, mpg) %>%
summarise(hp_mean=mean(hp),mpg_mean=mean(mpg))
```

__2.f__ Improve the summary statistics by also displaying the median, the minimum, the maximum, the standard deviation and the count.

```{r}
# 2.f

summarize(cars_cyl, mean(hp), mean(mpg), median(hp), median(mpg), min(hp), min(mpg), max(hp), max(mpg), sd(hp), sd(mpg))

# Function Count ne fonctionne pas 
```

__2.g__ Modify `cars_cyl` by adding a new variable called `perf = hp/mpg` and another
variable `rank` indicating the rank of the cars in terms of performance (the higher the better). 
Print out the resulting table by decreasing performance.

```{r}
# 2.g

cars_cyl <- cars_cyl %>% mutate(perf=hp/mpg,
rank = rank(-perf)) %>%
arrange(desc(perf))


```

__2.h__ Print out the average performance for each 
number of cylinders. What can you say about the relationship between the two variables?

```{r}
# 2.h

cars_cyl %>% summarise(perf_mean=mean(perf))

# Pourquoi il trouve pas perf ? 
```

__2.i__ Using the full dataset, plot the relationship between the weight and miles per US gallon, with a different color for each number of cylinder. What can you conclude about the relationships between the three variables? Bonus: add a (linear) regression line for each group.

```{r}
# 2.i
LR <- lm(wt~ mpg , data = mtcars)
library(ggplot2)
ggplot(data = mtcars, mapping = aes(x=wt, y=mpg), color=cyl) %>% 
geom_point()


# Faire la regression par catégorie de cylindre 

```

__2.j__ Using the full dataset, plot the performance (gross horsepower divided by miles per US gallon) as a function of the weight, with a different color for each number of cylinders and a different shape for each type of transmission. What can you conclude about the relationships 
between the four variables?

```{r}
# 2.j
select(mtcars)
perf = mtcars$hp/mtcars$mpg

```

__2.k__ Save `cars_cyl` as a `.csv` into the `results` subdirectory in your project.

```{r}
# 2.k

save

```

